Meta-analysis

### 2019-08-07 05_MetaAnalysis.Rmd
corrected conversion equation for stdev to sample variance

# Equation to convert standard deviation to Sampling Variance 
   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j]/
               sqrt(PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Replicates[j]))^2
   }

>>>>

# Equation to convert standard deviation to Sampling Variance 
   Sv[j] = (PM_MB_means[PM_MB_means$Trial_ref %in% Trials$Trial_ref,]$Yield_error[j])^2
   }
